### 2022-02-19 README.Rmd
Minor edits
Included ORCID

<!-- This repository contains the data and code for the paper: -->

<!-- > Authors, (YYYY). *`r Title`*. Name of journal/book -->
<!-- > <https://doi.org/xxx/xxx> -->

@@

>  Roalkvam, Isak (2021). *`r Title`*. Accessed
> `r format(Sys.Date(), "%d %b %Y")`. Online at
> <https://doi.org/10.31235/osf.io/cqaps>

### How to cite

>>>>

This repository contains the data and code for the paper:

> Roalkvam, Isak <a href="https://orcid.org/0000-0001-6974-1374"> <img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a> (2022). `r Title`. *Journal of Archaeological Science: Reports*
> <https://doi.org/10.1016/j.jasrep.2022.103371>

@@

>  Roalkvam, Isak (2022). *`r Title`*. Accessed
> `r format(Sys.Date(), "%d %b %Y")`. Online at
> <https://doi.org/10.31235/osf.io/cqaps>
